---
title: "p8105_hw6_yy2912"
author: "Roxana Yan"
date: "19/11/2019"
output: github_document
---
```{r setup, include=FALSE}
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r}
library(modelr)
library(tidyverse)
```

load data 
```{r, message=FALSE}
birthweight = 
  read_csv('./Data/birthweight.csv') 
```

#problem 1
clean data 

```{r}
birthweight_clean = 
  birthweight %>% 
  janitor::clean_names()%>%
  mutate(
    babysex = fct_infreq(as.factor(babysex)),
    frace = fct_infreq(as.factor(frace)),
    malform = fct_infreq(as.factor(malform)),
    mrace = fct_infreq(as.factor(mrace))
  )
```

the four numeric variabled have been converted to factor variables

```{r}
birthweight_clean %>% 
filter(is.na(bwt))
```
there is no missing data in this dataset

proposed model: 
the model I proposed include several factors that may associate with baby's birthweight. 
baby's birthweights may be associated with baby's sex, baby's head circumferences, mother's weight at delivery, mother’s age at delivery, mother’s pre-pregnancy BMI. 

```{r}
proposed_model = lm(bwt ~ babysex + bhead + delwt + momage + gaweeks + ppbmi, data = birthweight_clean)
```


```{r}
proposed_model %>% 
  broom::glance()%>%
  knitr::kable()

```

the overall model has a p-value of close to 0, which is smaller than alpha of 0.05, meaning that the model proposed is a reasonable model for the outcome, birthweight

```{r}
proposed_model %>% 
  broom::tidy()%>%
knitr::kable()
```

in addition, all predcitors included in the model have p-values smaller than alpha of 0.05, meaning that each of them is independtly associated with the outcome birthweight and the association is statistically significant.

```{r}
birthweight_clean %>% 
modelr::add_residuals(proposed_model) %>% 
modelr::add_predictions(proposed_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()+
  labs(
    title = 'Model residuals against fitted values',
    x = 'Fitted values',
    y = 'Residuals'
  )
```

compare two models

```{r}
model1 = lm(bwt ~ blength + gaweeks, data = birthweight_clean)
```

```{r}
model2 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex, data = birthweight_clean)
```


```{r}
library(mgcv)
```


```{r}
cv_df= crossv_mc (birthweight_clean, 100)%>%

  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_results=cv_df%>%
  mutate(proposed_model= map(train,~proposed_model),
         model1= map(train,~model1),
         model2= map(train,~model2)
         )%>%
  mutate(rmse_proposed_model = map2_dbl(proposed_model, test, ~rmse(model = .x, data = .y)),
         rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
         rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)))
```

```{r}
cv_results%>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

The violin graph shows the variance in prediction error across methods and model 2 has the smallest variance and is the best of the three. 


#problem 2

```{r, message=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

generate bootstrap samples 

```{r}
bootstrap_samples = 
  weather_df %>%
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results1 = map(models, broom::tidy), 
    results2 = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results1, results2) 
```

```{r}
bootstrap_samples_new=
bootstrap_samples %>%
  group_by(r.squared, adj.r.squared) %>% 
 summarize(log_beta = sum(log(estimate)))
```

the distribution of r squared 

```{r}
bootstrap_samples_new %>%
  ggplot(aes(x = r.squared)) +
  geom_density() +
labs(title = "The distribution of R Squared",
       x = "R Squared")

quantile(pull(bootstrap_samples, r.squared),c(0.025,0.975))

```

Based on the plot, r squared follows a normal distribution with a slight left skewedness.
The 95% CI of r squared lies between 0.8936 and 0.9274. 

the distribution of log(β^0*β^1)

```{r}
bootstrap_samples_new %>%
  ggplot(aes(x = log_beta)) +
  geom_density() +
  labs(title = "The distribution of log(β^0*β^1)", 
       x = "log(β^0*β^1)")

quantile(pull(bootstrap_samples_new, log_beta),c(0.025,0.975))
```

From the plot, log(β^0*β^1)  roughly follows a normal distribution.
The 95% CI of log(β^0*β^1)  lies between 1.9647 and 2.0579. 

